---
title: "Missing Data Homework"
author: "Dr. Michael Shepherd"
date: "10/21/2021"
output: html_document
---


*DUE WEDNESDAY 11:59pm*




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(VIM)
library(naniar)
library(dplyr)
library(ggplot2)
library(mice)
library(Zelig)
library(gridExtra)
library(Amelia)

```


# Load the freetrad data from Milner and Kubota (2005). This article studies the effect of democracy on trade policy. The data have been subset to nine countries in Asia from
1980 to 1999. This dataset includes 9 variables: year (year), country (country),
average tariff rates (tariff), Polity IV score (polity), total population (pop), gross
domestic product per capita (gdp.pc), gross international reserves (intresmi), a
dummy variable signifying whether the country had signed an IMF agreement in
that year (signed), a measure of financial openness (fivop), and a measure of US
hegemony. The Polity score is a number between -10 and 10 indicating how democratic a country is. A fully autocratic country would be a -10 while a fully democratic country would be a 10. This measure of US hegemony is the US imports and exports as a percent of the world total imports and exports.



```{r data}
data(freetrade)
```


# Question 1: Analyze the data for missingness. Which variables have missing data? How many observations are missing data? Are there combinations of variables that have missingness issues? Create a matrix plot showing the missingness issues facing this data set. 


```{r q1}

```

# Question 2: Calculate the correlation between the tariff and the fivop variables using "complete.obs". Create a well-labeled and designed scatterplot of the relationship between these two variables. Discuss your results. 



```{r q2}

```


# Question 3: Are there differences between observations missing and not missing the tariff variable in terms of level of democracy, population, and gross domestic product? 


```{r q3}

```


# Question 4: Use the Amelia package to impute missing data for the freetrade data set. Extract one of the imputations. Recalcuate the correlation between the tariff and the fivop variables. Create a well-labeled and designed scatterplot of the relationship between these two variables. Do the results differ from the original? If so, how? 


```{r q4}

```





# References 
Milner, Helen and Keiko Kubota. 2005. “Why the move to free trade? Democracy and trade policy in the developing countries.” International Organization. 59(1):107–143.