---
title: "Midterm_Makeup"
author: "Dr. Michael Shepherd"
date: "10/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(tidyverse)
library(tidytext)
library(ggplot2)
library(textdata)
```

  ## Processing data
1. Import your data into R
2. Perform any additional cleaning tasks as needed.

```{r}
# 1. Data on 3000 of Donald Trump's Tweets 2017-2018
load(url("https://cbail.github.io/Trump_Tweets.Rdata"))

```


For tips and tools on how to clean up difficult text data, please visit the TidyText website here: https://www.tidytextmining.com/tidytext.html

 
## Word count
1. Tokenize your corpus and generate a word count.
2. Using the `TidyText` package, remove stop words and generate a new word count.
3. Create a visualization of the word count distribution and interpret your results.


```{r}


```


## Tf-idf
1. Generate a tf-idf measure of words in your dataset.
2. Create a visualization of the tf-idf measure and interpret your results.
3. Is the basic word count or the tf-idf more appropriate for your analysis?


```{r}


```


## Sentiment analysis
1. Using the built-in sentiments from `TidyText`, generate sentiment counts for your words using either the basic word count or tf-idf measure from above.
2. Create a visualization of the sentiment measure. Interpret your results.

```{r}


```






